Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-06 paper/paper.Rmd
Fix ES plot axes

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE) +
  xlab("Orig. effect size (d)") + 
  ylab("Rep. effect size (d)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size(name = "Rep. N") +
  # scale_color_solarized(guide = FALSE)
  scale_color_solarized(name = "Subjective rep. rating")

>>>>

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE) +
  xlab("Orig. effect size (d)") + 
  ylab("Rep. effect size (d)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size(name = "Rep. N") +
  # scale_color_solarized(guide = FALSE)
  scale_color_solarized(name = "Subjective rep. rating")
